\chapter{Summary}\label{chapter:summary}

The open architecture of the proposed ticketing system benefits all stakeholders in the system. Event guests profit from fair ticketing pricing even on the aftermarket. Tickets cannot be sold for higher prices than the original cost of a ticket. Ticket scalpers have no scope of action and are prohibited on the protocol level to benefit from the inefficiencies of today's ticketing market.

Since the data on Ethereum is publicly available, anyone can build an interface and become a GUI provider. GUI providers are incentivised to build appealing frontend applications in order to attract more users. They are compensated with every ticket sale that is initiated from their platform. A fair market of attractive and user-friendly frontend applications that connect to the same data can emerge.

With this open design, event guests can connect to their favourite ticketing GUI provider and they do not need to check whether a ticket for the same event is offered on any other platform since they all connect to the same data. The queuing architecture enables buyers and sellers to transact with each other. Also, there is no trust needed when exchanging a ticket on the aftermarket. The seller cannot fool the buyer by not sending the ticket after receiving the money. The SC guarantees that the ownership is only transferred if the correct amount of money is sent.

Furthermore, the proposed architecture creates a new market for ID approvers which are needed in a decentralized system since there are no restrictions from creating a wallet and interacting with the platform. ID approvers are incentivised to act trustworthy since they are financially compensated if they are chosen by the event hosts. Their approval on the BC can even be integrated into other services on the Ethereum BC. 

The social trust certificates creates a layer of trust that is higher than in current online ticket platforms without the need of a trusted third party. Aggregating ownership proofs across multiple social profiles in the event listing increases the legitimacy of an event. 

The proposed presale design guarantees a fair distribution if the demand for an event is higher than its supply. The lottery is transparent and publicly available. Furthermore, it prevents front running attacks and should not lead to sudden surges in gas prices.

An event host can specify which currency is used for buying tickets. Specifically, ETH and any ERC20 token can be used as a mean of payment. There are many different implementations of stable-coins in the Ethereum ecosystem. By allowing any ERC20 token to be specified, the host is not exposed to the price fluctuations of the volatility of ETH.

The guest-client web application allows users to buy tickets once the initial hurdle of setting up an Ethereum wallet for a non technical user is overcome. The integrated and tightly coupled aftermarket provides a novelty function that is not available on most ticketing platforms as of today. Through this, both the question of validity when buying a ticket from another user, as well as the inflated prices on tickets with high demand are addressed. The guest-client application provides a user-friendly interface to all building blocks of the proposed SC-based ticketing platform.

With the host-client web application, hosts can easily create and manage their events and retrieve useful information about its state. It allows event hosts to interact with the event and identity contracts without needing to know or learn much about the BC technology, apart from knowing how to create and handle an Ethereum wallet.

One of the main goals of the suggested architecture is to prohibit scalpers from misusing the secondary market of the ticketing industry for their own profit. To achieve this, the design proposes to verify the identity of the guests. Only verified accounts can buy tickets from the SC. This crucial part of identifying and approving the identity of a guest and linking the identity to an Ethereum address is done by the ID approver application. As the proposed implementation is just an example and the identity SC is used to store the identities, every entity may act as an ID approver.

To provide a solution for the full life-cycle of a ticket, an access control application, and an access terminal have been designed and implemented. These applications are used to check a guest's ownership of a required ticket and they guarantee that only guests, that are holding a valid ticket, may enter the event. The process of invalidating tickets is done off-chain due to scalablilty limitations of the Ethereum BC. The off-chain invalidation requires that tickets cannot be resold after they have been used to enter the venue. A passive invalidation mechanism is implemented in the SC making it impossible to resell a ticket after the doors have opened to the venue. 

Most of the requirements described in Chapter \ref{chapter:introduction:descriptionOfWork} are implemented or a detailed explanation is given why a different design is chosen. The proof of concept has shown that BC technology has the possibility to eliminate many of the inefficiencies that exist in today's ticketing industry. However, BC technology is not the holy grail for the stated problems and introduces other challenges instead. In the following section, some of the challenges are described as future research topics. 
