\section{Access Control}
% author: Nicolas Spielmann
The access control application is used to check, whether a guest is eligible to enter the event. To be eligible to enter, the guest needs to hold the right amount of the right type of tickets. This check needs to be done very fast, since a guest does not want to wait for the validity check when entering the venue and usually many guest should enter the venue within a short time frame. This could be tackled by doing the whole check of ticket ownership and invalidation off-chain. However, due to the implementation of the event SC, it is not trivial to obtain all current owner of a ticket and just save them to a database. Therefore, a hybrid approach was chosen.

This hybrid approach makes use of the fact, that once the Ethereum address is known, it is trivial to check for ticket ownership. The BC is only queried to obtain the amount of ticket the guest holds. Since this is a pure view transaction, this can be done very fast and does not cost anything. To make this query even faster, a local BC node could be run.

To ensure that guest can only enter once with the ticket, it is locally saved, how many tickets per Ethereum address entered to the event. When determine, whether a guest still has enough tickets, the local database and the BC are queried to calculate the number of remaining tickets. This also solves the problem of invalidation of tickets, since the ticket is considered as used, once it has been saved to the local database. An invalidation of tickets on-chain would have come with a very high cost, since all the tickets would require an Ethereum transaction to invalidate them, costing GAS payed by the event host.
