\section{Thesis Outline}

The following paragraph will provide a short outline over the thesis' sections and their respective content. Firstly, in order to create context to existing approaches of distributing tickets on the BC a set of related projects is discussed. For each project, implementation specific details are listed and in \ref{tab:overview-competitors} important properties for both end users and event organizers are compared. Afterwards the design philosophy for all individual parts of the Idetix ticketing platform is introduced. This includes choices both in terms of data modelling, architecture, and SC implementation as well as design aspects of GUIs for the web applications. This section also explains how all non decentralized parts of the platform work and how they plug into the ecosystem. In Chapter 4, implementation details to all building blocks of the platform are discussed and put into perspective with their impact on the functionality and usability of the product. This includes technical choices for data storage both on- and off-chain as well as data fetching from the BC. Chapter 5 provides evaluations of the platform in two major ways. First, surveys for both event hosts and event guests are introduced alongside with their results. Secondly performance evaluations on SC interactions, the identity approval service, and the data fetching mechanisms for the client applications are provided. Chapter 6 and 7 provide a summary of the project and possible extensions for future work, respectively.